\hydrogen{} and \carbon{} Network Strategies for the European Energy System

### 2023-12-29 report/submissions/journal/paper/paper.tex
add reproducibility link

\subsection*{Acknowledgements}

Fabian Hofmann and Christoph Tries are funded by the Breakthrough Energy Initiative (\href{https://breakthroughenergy.org/}{https://breakthroughenergy.org/}).

>>>>

\subsubsection*{Reproducibility}

The workflow to reproduce all figures and numbers is available at \href{https://github.com/FabianHofmann/carbon-networks}{github.com/FabianHofmann/carbon-networks}.

\subsubsection*{Acknowledgements}

Fabian Hofmann and Christoph Tries are funded by the Breakthrough Energy Initiative (\href{https://breakthroughenergy.org/}{breakthroughenergy.org}).
